
\section{Introduction [Md Jahidul Haque]}
Software  releasing  process  can  be  procedural  in  the  conventional  software  development life-cycle(SDLC). In traditional SDLC, the software development mostly depends on the different development teams working on the different parts of the same project.  Ideally,developers  need  to  collaborate  between  themselves  to  mitigate  the  knowledge  gaps  to ensure a successful release of the software.  During the software releasing process, the code review of any changes in the existing software is very crucial in SDLC. After reviewing the code by the code review team, the new changes in the code is inspected but he testing team for the quality assurance of the new changes.  This new changes is then passes through various unit testing and integration testing by the testing team.  Furthermore,  the QA passed  patch  of  the  software  is  handed  over  the  deployment  team  who  are  responsible for  the  releasing  the  new  version  of  the  software.   This  involves  DevOps  tasks  for  the deployment team.  The DevOps engineers create and manage different cloud services to provision and scale the software deployment during the release.  After Provisioning and scaling the new version of the software is released.

The cloud-native architecture suggest software release via public clouds like AWS, Google Cloud or the Microsoft Azure. Also, this approach overcome the various hurdles of setting up on-premise infrastructure. Yet, the public cloud based software development  suffers vendor lock-in issues. In the traditional way of software release described in the previous paragraph, managing cloud-native application is much tougher to provision and scale manually for the deployment team. This creates time lagging in SDLC for any new modification of the software. In this particular case, CI/CD comes in practice among the software development community. CI/CD stands for continuous integration and continuous deployment/delivery. In this novel approach, SDLC can achieve more granular gain from the resource optimization during the release process of the software. Moreover, this process helps developers to automate tests and make QA process more free from human errors. 


The Continuous integration of the cloud-native application means the automation of the software releasing process via automation of various SDLC processes. For example, the automation in the repository management in continuous integration reefers to development of automation scripts that can automatically handle any new changes of the repository of a application code-base. These automation scripts can be handled different technologies like Gihub Actions, GitLab CI/CD, Jenkins, CircleCI. For public cloud like the AWS or the Azure, Github or GitLab can be used by the developers to developer automation scripts for managing the repository in the case of modification or new release of the software.

Continuous deployment in SDLC involves the automation of the software release process via configuration scripts in deployment automation technologies. Github offers Github Actions feature which is the main platform for describing the continuous deployment process. Gihub offers developers to develop their release process via Github's own domain specific language (DSL). Github's DSL supports {{.yml}} scripts to write github workflows. Github Workflow enables various jobs for deployment inside the development environment. Developers can manage their repository and create automated tasks to serialize the batch processes during the deployment. The main purpose of this continuous deployment is initiate the continuous integration smoothly without the manual configuration of the repository. After conducting all the acceptance testing the automation jobs can also create new dependencies via the {{.yml}} files. But the continuous deployment lacks the infrastructure automation which brings the manual configuration of the public cloud infrastructure. This technological need brings the concept of continuous delivery.

Continuous delivery refers to deployment automation when developer is able to automate the cloud infrastructure via the infrastructure automation objects. This enables the developer to manage,provision and scale the whole infrastructure which is needed for their developed software. In the infrastructure automation process, Github Action also involves for managing the pipeline where services in AWS are responsible for creating the infrastructure objects. The main technology of continuous delivery is CloudFormation from AWS. CloudForamtion is a complete infrastructure automation tool for continuous delivery of a software. 

In this report we will talk about the implementation of the automation of the software release for the spring-boot application. At the beginning of the implementation we have a spring-boot application which have several services exposed and the application is using Gradle package management for dependency management. In our implementation, we will implement continuous by developing a CI pipeline for integrating the application in AWS and Azure cloud services. Our implementation involves two major parts: continuous integration (CI) and continuous deployment/delivery. For both the cases of CI and CD, we will discuss two different pipeline implementation: one for Azure and another one for AWS cloud. 

\input{sections/Shoaib/introduction_motivation}