

\subsection{Testing}\label{sec:Testing}

\textit{Author: Wakeel Khan}

\subsubsection{What is Testing}

Testing is the process of analyzing the authenticity of the lines of instructions known as code to check if the product or software is fulfilling the requirements. Or it can be said, process of testing verifies and makes sure that the underlying software is fitting on the expected requirements of the user or client. Suppose you entered a backing contest, and you are planning to make a cookie. Chances are you will first make small batch of cookies to test how good your recipe is and if everything is well and fine as you expected to be. Well, depending on the feedback you received about the taste and other qualities of the cookie. you will then modify your recipe and proceed for further cooking.\par

Testing is somewhat similar in that sense. Well, after programmer or a team of programmer write a software program. There are information technology professionals known as tester who then test the software to see if there are any areas where the software crashes or does not work as expected, that is all testing is all about.

\subsubsection{Importance of Testing}

Bugs are an unfortunate reality for every software products. In there are lot of risk involved in software, by risk I just mean anything that can potentially cause a loss of something of value this can include functionally issues, scalability issues, reliability issues, security issues or performance issues or any other thing. Unfortunately, sometime these issues manifest into software disaster and have cost millions of dollars as in waste and sometimes even lead to causalities. \par

For Example, Starbucks famous coffee shop was forced to give away free drinks just because of registered malfunctions, So this caused company lots of financial loss. \footnote{https://www.geekwire.com/2015/starbucks-lost-millions-in-sales-because-of-a-system-refresh-computer-problem/} F35 Military Aircraft was unable to detect the target correctly because of radar failure. \footnote{https://www.military.com/defensetech/2015/03/24/software-glitch-causes-f-35-to-incorrectly-detect-targets-in-formation} Similarly, in 1985 Canada's Therac-25 Radiation Therapy machine detects malfunction due to some software bugs and it delivered lethal radiations to patients and it cause 3 people dead and critically injured many other patients. \footnote{https://www.bugsnag.com/blog/bug-day-race-condition-therac-25} So, considering all the aforementioned scenarios we came to conclusion that testing is an integral part of Software Development Life Cycle (SDLC).











